AggregateCounts

### 2021-09-09 R/AggregateCounts.Rmd
added stats and simplified figure 1D and 2D

#Get aggregate Summary per condition and region
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))
```
```{r Overview Plots}
#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
#####
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

```
```{r figures 1A,1B and 2A, 2B}
#Biomass wt
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#Biomass Sa and mutants
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Culture=="co"),
                                aggregateListSummaryReplicate%>% filter(Culture=="co"),
                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")

@@

HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
#Summary data frame
HistCondRegionSum<-HistConditionRegin %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####
```

>>>>

#Get aggregate Summary per condition and region
aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))

#T-tests for biomass and Aggs
TtestTable<-name <- function(dataPoint) {data <-data.frame(dataPoint$data.name, dataPoint$p.value)}
##WT co vs mono comparisons
###Biomass and Aggs of Pa mono vs co
PaWtmono<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono")
PaWtco<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co")
PaWtonovsCoBiomassTtest<-t.test(x = PaWtmono$biomass, y = PaWtco$biomass, paired = F)
PaWtonovsCoAggsTtest<-t.test(x = PaWtmono$Aggs, y = PaWtco$Aggs, paired = F)
###Biomass and Aggs of Sa mono vs co
SaWtmono<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "Sa", Culture == "mono")
SaWtco<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "wt", Culture == "co")
SaWtonovsCoBiomassTtest<-t.test(x = SaWtmono$biomass, y = SaWtco$biomass, paired = F)
SaWtonovsCoAggsTtest<-t.test(x = SaWtmono$Aggs, y = SaWtco$Aggs, paired = F)
###Biomass and Aggs of Pa core vs edge co-culture
PaWtCoEdge<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "edge")
PaWtcoCore<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "core")
PaWtCoEdgevsCoreBiomassTtest<-t.test(x = PaWtCoEdge$biomass, y = PaWtcoCore$biomass, paired = F)
PaWtCoEdgevsCoreAggsTtest<-t.test(x = PaWtCoEdge$Aggs, y = PaWtcoCore$Aggs, paired = F)
###Biomass and Aggs of Sa core vs edge co-culture
SaWtCoEdge<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "edge")
SaWtcoCore<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "core")
SaWtCoEdgevsCoreBiomassTtest<-t.test(x = SaWtCoEdge$biomass, y = SaWtcoCore$biomass, paired = F)
SaWtCoEdgevsCoreAggsTtest<-t.test(x = SaWtCoEdge$Aggs, y = SaWtcoCore$Aggs, paired = F)

tTestFigs1ABData<-list(PaWtonovsCoBiomassTtest,PaWtonovsCoAggsTtest,PaWtCoEdgevsCoreBiomassTtest,PaWtCoEdgevsCoreAggsTtest,
                       SaWtonovsCoBiomassTtest,SaWtonovsCoAggsTtest,SaWtCoEdgevsCoreBiomassTtest,SaWtCoEdgevsCoreAggsTtest)
tTestFigs1ABTable<-bind_rows(map(tTestFigs1ABData, TtestTable))
##co wt vs mutants
###Biomass and Aggs of Pa wt vs mutants
PaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
PaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
###Biomass and Aggs of Sa wt vs mutants
SaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
SaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
summary(PaAggsAov)
TukeyHSD(PaAggsAov)#wt~pqsL p = 0.06, wt~phz p = 0.003
summary(SaAggsAov)
TukeyHSD(SaAggsAov)#wt~pqsL p = 0.03

```{r biomass, aggregate number and mean size Plots}
#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(Species~Culture, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  scale_color_brewer(palette = "Set1")+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
#####
#Plot only biomass per Sample
#####
PlotBiomasPerSample<-function(df){
ggplot()+ 
    #this is for multiple conditions
  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      #this is for multiple conditions  
    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
    #this is for only one mutant
    facet_grid(.~TimePoint, scales = "free", space = "free") +
  ggtitle('Total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(1, 2,0))+
  theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

```{r figures 1A,1B and 2A, 2B}
#Biomass wt
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#Biomass Sa and mutants
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Culture=="co"),
                                aggregateListSummaryReplicate%>% filter(Culture=="co"),
                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")

@@

HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
#Summary data frame
HistCondRegionSum<-HistConditionRegin %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####

#Stats for aggregates
##Mono vs Co
PaMono5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(.5, 5]")
PaCo5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(.5, 5]")
PaMono10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(5, 10]")
PaCo10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]")
PaMono100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(10, 100]")
PaCo100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(10, 100]")

PaMonoCo5BiomassTtest <-t.test(x = PaMono5$NormalizedBiomass, y = PaCo5$NormalizedBiomass, paired = F)
PaMonoCo5FreqTtest    <-t.test(x = PaMono5$NormalizedFrequency, y = PaCo5$NormalizedFrequency, paired = F)
PaMonoCo10FreqTtest   <-t.test(x = PaMono10$NormalizedFrequency, y = PaCo10$NormalizedFrequency, paired = F)
PaMonoCo100FreqTtest  <-t.test(x = PaMono100$NormalizedFrequency, y = PaCo100$NormalizedFrequency, paired = F)

SaMono5<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(.5, 5]")
SaCo5<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]")
SaMono10<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(5, 10]")
SaCo10<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(5, 10]")
SaMono100<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(10, 100]")
SaCo100<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(10, 100]")

SaMonoCo5BiomassTtest <-t.test(x = SaMono5$NormalizedBiomass, y = SaCo5$NormalizedBiomass, paired = F)
SaMonoCo5FreqTtest    <-t.test(x = SaMono5$NormalizedFrequency, y = SaCo5$NormalizedFrequency, paired = F)
SaMonoCo10FreqTtest   <-t.test(x = SaMono10$NormalizedFrequency, y = SaCo10$NormalizedFrequency, paired = F)
SaMonoCo100FreqTtest  <-t.test(x = SaMono100$NormalizedFrequency, y = SaCo100$NormalizedFrequency, paired = F)

tTestFigs1CDData<-list(PaMonoCo5BiomassTtest,PaMonoCo5FreqTtest,PaMonoCo10FreqTtest,PaMonoCo100FreqTtest,
                       SaMonoCo5BiomassTtest,SaMonoCo5FreqTtest,SaMonoCo10FreqTtest,SaMonoCo100FreqTtest)
tTestFigs1CDTable<-bind_rows(map(tTestFigs1CDData, TtestTable))
### Edge vs Core
Pawt5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "wt", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
Pawt5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]",Region == "core")
Pawt10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "edge")
Pawt10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "core")
Pawt100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "edge")
Pawt100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "core")

Sawt5E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
Sawt5C<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture=="co",LogBin =="(.5, 5]",Region == "core")
Sawt10E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]",Region == "edge")
Sawt10C<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]",Region == "core")
Sawt100E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4",Strain == "wt", Culture=="co",LogBin=="(10, 100]",Region== "edge")
Sawt100C<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint=="Day 4",Strain=="wt",Culture == "co",LogBin == "(10, 100]",Region == "core")

Pawt5CorEdBioTtest     <-t.test(x = Pawt5E$NormalizedBiomass, y = Pawt5C$NormalizedBiomass, paired = F)
Pawt5CorEdFreqTtest    <-t.test(x = Pawt5E$NormalizedFrequency, y = Pawt5C$NormalizedFrequency, paired = F)
Pawt10CorEdFreqTtest   <-t.test(x = Pawt10E$NormalizedFrequency, y = Pawt10C$NormalizedFrequency, paired = F)
Pawt100CorEdFreqTtest  <-t.test(x = Pawt100E$NormalizedFrequency, y = Pawt100C$NormalizedFrequency, paired = F)

Sawt5CorEdBioTtest     <-t.test(x = Sawt5E$NormalizedBiomass, y = Sawt5C$NormalizedBiomass, paired = F)
Sawt5CorEdFreqTtest    <-t.test(x = Sawt5E$NormalizedFrequency, y = Sawt5C$NormalizedFrequency, paired = F)
Sawt10CorEdFreqTtest   <-t.test(x = Sawt10E$NormalizedFrequency, y = Sawt10C$NormalizedFrequency, paired = F)
Sawt100CorEdFreqTtest  <-t.test(x = Sawt100E$NormalizedFrequency, y = Sawt100C$NormalizedFrequency, paired = F)

tTestFigs2ABDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
                       Sawt5CorEdBioTtest,Sawt5CorEdFreqTtest,Sawt10CorEdFreqTtest,Sawt100CorEdFreqTtest)

tTestFigs2ABTableCorEdge<-bind_rows(map(tTestFigs2ABDataCorEdge, TtestTable))

##wt vs mutants
# Compute the analysis of variance 
Pabiomass5Aov <- aov(NormalizedBiomass ~ Strain, data = HistReplicateSummary%>%
                     filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Pafrequency5Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Pafrequency10Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
Pafrequency100Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
##None of the Pa are significant
Sabiomass5Aov <- aov(NormalizedBiomass ~ Strain, data = HistReplicateSummary%>%
                     filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]")) 
Safrequency5Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Safrequency10Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
Safrequency100Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))

summary(Pabiomass5Aov)
TukeyHSD(Pabiomass5Aov)
# Summary of the analysis
summary(Sabiomass5Aov)#*p = 0.07
TukeyHSD(Sabiomass5Aov)#*p pqsL-wt 0.077
summary(Safrequency10Aov)#*p = 0.005
TukeyHSD(Safrequency10Aov)#*p pqsL-wt 0.003

#now compute comparison edge vs core
PaPhz5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "phz", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPhz5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "phz",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPhz10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPhz10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "core")
PaPhz100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "edge")
PaPhz100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "core")
PaPqsL5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPqsL5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPqsL10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPqsL10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain =="pqsL",Culture =="co",LogBin == "(5, 10]",Region == "core")
PaPqsL100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture=="co",LogBin =="(10, 100]",Region == "edge")
PaPqsL100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture=="co",LogBin=="(10, 100]",Region == "core")

PaPhz5CorEdBioTtest     <-t.test(x = PaPhz5E$NormalizedBiomass, y = PaPhz5C$NormalizedBiomass, paired = F)
PaPhz5CorEdFreqTtest    <-t.test(x = PaPhz5E$NormalizedFrequency, y = PaPhz5C$NormalizedFrequency, paired = F)
PaPhz10CorEdFreqTtest   <-t.test(x = PaPhz10E$NormalizedFrequency, y = PaPhz10C$NormalizedFrequency, paired = F)
PaPhz100CorEdFreqTtest  <-t.test(x = PaPhz100E$NormalizedFrequency, y = PaPhz100C$NormalizedFrequency, paired = F)
PaPqsL5CorEdBioTtest     <-t.test(x = PaPqsL5E$NormalizedBiomass, y = PaPqsL5C$NormalizedBiomass, paired = F)
PaPqsL5CorEdFreqTtest    <-t.test(x = PaPqsL5E$NormalizedFrequency, y = PaPqsL5C$NormalizedFrequency, paired = F)
PaPqsL10CorEdFreqTtest   <-t.test(x = PaPqsL10E$NormalizedFrequency, y = PaPqsL10C$NormalizedFrequency, paired = F)
PaPqsL100CorEdFreqTtest  <-t.test(x = PaPqsL100E$NormalizedFrequency, y = PaPqsL100C$NormalizedFrequency, paired = F)

SaPhz5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
SaPhz5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "core")                                        
SaPqsL5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
SaPqsL5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "core")
SaPhz10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPhz10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPqsL10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPqsL10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPhz100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPhz100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPqsL100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPqsL100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPhz5CorEdBioTtest     <-t.test(x = SaPhz5E$NormalizedBiomass, y = SaPhz5C$NormalizedBiomass, paired = F)
SaPhz5CorEdFreqTtest    <-t.test(x = SaPhz5E$NormalizedFrequency, y = SaPhz5C$NormalizedFrequency, paired = F)
SaPhz10CorEdFreqTtest   <-t.test(x = SaPhz10E$NormalizedFrequency, y = SaPhz10C$NormalizedFrequency, paired = F)
SaPhz100CorEdFreqTtest  <-t.test(x = SaPhz100E$NormalizedFrequency, y = SaPhz100C$NormalizedFrequency, paired = F)
SaPqsL5CorEdBioTtest     <-t.test(x = SaPqsL5E$NormalizedBiomass, y = SaPqsL5C$NormalizedBiomass, paired = F)
SaPqsL5CorEdFreqTtest    <-t.test(x = SaPqsL5E$NormalizedFrequency, y = SaPqsL5C$NormalizedFrequency, paired = F)
SaPqsL10CorEdFreqTtest   <-t.test(x = SaPqsL10E$NormalizedFrequency, y = SaPqsL10C$NormalizedFrequency, paired = F)
SaPqsL100CorEdFreqTtest  <-t.test(x = SaPqsL100E$NormalizedFrequency, y = SaPqsL100C$NormalizedFrequency, paired = F)

tTestFigs2CDData<-list(PaPhz5CorEdBioTtest,PaPhz5CorEdFreqTtest,PaPhz10CorEdFreqTtest,PaPhz100CorEdFreqTtest,
                       PaPqsL5CorEdBioTtest,PaPqsL5CorEdFreqTtest,PaPqsL10CorEdFreqTtest,PaPqsL100CorEdFreqTtest,
                       SaPhz5CorEdBioTtest,SaPhz5CorEdFreqTtest,SaPhz10CorEdFreqTtest,SaPhz100CorEdFreqTtest,
                       SaPqsL5CorEdBioTtest,SaPqsL5CorEdFreqTtest,SaPqsL10CorEdFreqTtest,SaPqsL100CorEdFreqTtest)

tTestFigs2CDTable<-bind_rows(map(tTestFigs2CDData, TtestTable))
